### 2020-02-08 cv_models.tex
updated main sections

\section{Comparison across series of CV models}
\label{sxn:cv}

@@

\paragraph{Coarse Analysis: Quality Metrics versus Reported Test Accuracies.}

We have examined the performance of the four quality metrics (Log Frobenius norm, Log Spectral norm, Weighted Alpha, and Log $\alpha$-Norm) applied to each of the VGG, ResNet, ResNet-1K, and DenseNet series.
To start, Figure~\ref{fig:vgg-metrics} considers the VGG series (in particular, the pretrained models VGG11, VGG13, VGG16, and VGG19, with and without BatchNormalization), and it plots the four quality metrics versus the reported Test accuracies~\cite{pyTorchVgg}, as well as a basic linear regression line. 
%with the Root Mean Squared Error (RMSE) shown, \michael{XXX.  WHERE IS RMSE.  IN THAT TABLE?}
All four metrics correlate quite well with the reported Top1 Accuracies, with smaller norms and smaller values of $\hat{\alpha}$ implying better generalziation (i.e., greater accuracy, lower error). 
While all four metrics perform well, notice that the Log $\alpha$-Norm metric ($\log\Vert\mathbf{W}\Vert_{\alpha}^{\alpha}$) performs best (with an RMSE of $0.42$, see Table~\ref{table:cv-models}); and the Weighted Alpha metric ($\hat\alpha =\alpha\log\lambda_{max} $), which is an approximation to the Log $\alpha$-Norm metric~\cite{MM20_unpub_work}, performs second best (with an RMSE of $0.48$, see Table~\ref{table:cv-models}).

@@

\begin{table}[t]
\small
\begin{center}
%\begin{tabular}{|p{1in}|c|c|c|c|c|}
\begin{tabular}{|p{0.75in}|c|c|c|c|c|}
%\begin{tabular}{|l|c|c|c|c|c|}
\hline
 Series    &\#   & $\log\langle\Vert\mathbf{W}\Vert_{F}\rangle$ & $\log\langle\Vert\mathbf{W}\Vert_{\infty}\rangle$ & $\hat{\alpha}$ & $\log\langle\Vert\mathbf{X}\Vert^{\alpha}_{\alpha}\rangle$ \\
\hline
 VGG       &  6 & 0.56 & 0.53 & 0.48          & \textbf{0.42}  \\
 ResNet    &  5 & 0.9  & 1.4  & \textbf{0.61} & 0.66           \\
 ResNet-1K & 19 & 2.4  & 3.6  & \textbf{1.8}  & 1.9            \\
 DenseNet  &  4 & 0.3  & 0.26 & \textbf{0.16} & 0.21           \\
\hline
\end{tabular}
\end{center}
\caption{RMSE (smaller is better) for linear fits of quality metrics to Reported Top1 Test Error for pretrained models in each architecture series.  VGG, ResNet, and DenseNet were pretrained on ImageNet, and ResNet-1K was pretrained on ImageNet-1K. 
\michael{Are the numbers in this table stale; if they get updated, then we need to modify the test at at least two places, on actual numbers and on what is best.}
}
\label{table:cv-models}
\end{table}

@@

More generally, we can understand Figure~\ref{fig:vgg-alpha-layers} in terms of the \emph{flow of correlation}, as follows.
Recall that the Log $\alpha$-Norm metric and the Weighted Alpha metric are based on HT-SR Theory~\cite{MM18_TR, MM19_HTSR_ICML, MM20_SDM}, which is in turn based on ideas from the statisical mechanics of heavy tailed and strongly correlated systems~\cite{BouchaudPotters03, SornetteBook, BP11, bun2017}. 
There, one expects well-trained systems which exhibit correlations over many size scales to have ESDs that can be well-fit by PLs, with PL exponents $\alpha\approx 2$.
Much larger values of $\alpha$ indicate very poor fits, but the presence of many adjacent layers with relatively good PL fits \emph{suggests} that those adjacent layers ``impedance match'' well and that the correlations that are captured by one layer propagate well to subsequent layers.
Informally, one would expect a DNN model to perform well when it fascilitates the propagation of information/features across layers.
In the absence of training/test data, we can to try to quantify this by measuring the PL properties of empirical weight matrices.
Smaller $\alpha$ values correspond to layers in which correlations across multiple scales are better captured~\cite{MM18_TR,SornetteBook}, and thus we expect that small values of $\alpha$ that are stable across multiple layers enable better \emph{correlation flow} through the network.

%\paragraph{Layer Analysis: Behavior on Less Thoroughy Studied CV Models.}
\paragraph{Corraltion Flow: PL vs. Norm Metrics.}

@@

\begin{figure}[t]
   \centering
   \subfigure[$\lambda_{max}$ for ResNet20 layers]{
      %\includegraphics[scale=0.14]{img/resnet4d_maxev.png}
      \includegraphics[width=4.0cm]{img/resnet4d_maxev.png}
      %\includegraphics[width=4.5cm]{img/resnet4d_maxev.png}
      \label{fig:resnet204Dalpha}
   }
   %\qquad
   \subfigure[$\alpha$ for ResNet20 layers]{
      %\includegraphics[scale=0.14]{img/resnet4d_alphas.png}
      \includegraphics[width=4.0cm]{img/resnet4d_alphas.png}
      %\includegraphics[width=4.5cm]{img/resnet4d_alphas.png}
      \label{fig:resnet204Dmaxev}
   }
   \caption{Correlation Flow.
            ResNet20, distilled with Group Regularization, as implemented in the \texttt{distiller} (4D\_regularized\_5Lremoved) pre-trained models.  
            Spectral Norm, $\log\lambda_{max}$, and, PL exponent, $\alpha$, for individual layer, versus layer id, for both baseline (before distillation, green) and finetuned (after distillation, red) pre-trained models. 
           }
   \label{fig:resnet204D5L}
\end{figure}

We consider ResNet20, trained on CIFAR10, before and after applying the Group Regularization technique, as implemented in the \texttt{distiller} package.%
\footnote{For details, see \url{https://nervanasystems.github.io/distiller/\#distiller-documentation} and also \url{https://github.com/NervanaSystems/distiller}.}
We analyze the available pre-trained 4D\_regularized\_5Lremoved baseline and fine-tuned models.  %\cite{distiller_repo}.
The reported baseline test accuracies ($Top1=91.45$ and $Top5=99.75$) are better than the reported fine-tuned test accuracies ($Top1=91.02$ and $Top5=99.67$)~\cite{XXX-XXX}.
The previous results on ResNet (Table~\ref{table:cv-models} and Figure~\ref{fig:cv2-accuracy} might suggest that the baseline Spectral Norm should be \emph{smaller} than those of the layers in the fine-tuned model.
\michael{Do we have something backwards here: where we observed that the average norm to increase with decreasing test error (as it ``should'' not), whereas the average PL exponent $\alpha$ decreases (as ``expected'' from HT-SR Theory).  }
In both cases (Frobenius norm results not shown), we observe the opposite.
Figure~\ref{fig:resnet204D5L} presents the Spectral Norm ($\lambda_{max}$) and PL exponent ($\alpha$) for each individual layer weight matrix $\mathbf{W}_{l}$.%
\footnote{Here, we only include layer matrices or feature maps with $M\ge50$.}
On the other hand, the $\alpha$ values do not differ systematically between the baseline and fine-tuned models.
\michael{Some comment about big jump in norm; but fix previous backwards question first.}
Also (not shown), the average (unweighted) baseline $\alpha$ is \emph{smaller} than the fine-tuned average (as would be predicted by HT-SR Theory, on which $\hat{\alpha}$ is based).

\michael{XXX.  WORK ON THIS PAR AFTER DO NLP EXAMPLES.}
Our interpretation of this is the following.
The pre-trained models in the \texttt{distiller} package have passed some quality metric, but they are much less well trodden than any of the VGG/ResNet/DenseNet models we condisered previously.
\charles{MOvE THIS SOMEWHERE ELSE AND CLEAN UP THIS SECTION Notice while norms make good regularizers for a single model, there is no reason \emph{a priori} 
to expect them correlate so well with the test accuracies across different models.
However, we do expect the PL $\alpha$ to do so because it effectively measures the amount of correlation in the model}
%
The reason for this is that the \texttt{distiller} Group Regularization technique 
%%has the unusual effect of increasing
\nred{spuriously increases}
 the norms of the $\mathbf{W}$ pre-activation maps for at least two of the Conv2D layers.
\michael{This impedance shuffling or whatever it is called messes up norms, but the strong correlations are still preserved, as seen in the $\hat{\alpha}$ metric, and the model quality is good.  CLARIFY.}
\michael{XXX.  INTERPRET IN TERMS OF XXX GOOD VERSUS BAD, AS OPPOSED TO GOOD BETTER BEST.}

>>>>

\section{Comparison of CV models}
\label{sxn:cv}

@@

\paragraph{Average Quality Metrics versus Reported Test Accuracies.}
We have examined the performance of the four quality metrics (Log Frobenius norm, Log Spectral norm, Weighted Alpha, and Log $\alpha$-Norm) applied to each of the VGG, ResNet, ResNet-1K, and DenseNet series.
To start, Figure~\ref{fig:vgg-metrics} considers the VGG series (in particular, the pretrained models VGG11, VGG13, VGG16, and VGG19, with and without BatchNormalization), and it plots the four quality metrics versus the reported Test accuracies~\cite{pyTorchVgg}, as well as a basic linear regression line. 
%with the Root Mean Squared Error (RMSE) shown, \michael{XXX.  WHERE IS RMSE.  IN THAT TABLE?}
All four metrics correlate quite well with the reported Top1 Accuracies, with smaller norms and smaller values of $\hat{\alpha}$ implying better generalziation (i.e., greater accuracy, lower error). 
While all four metrics perform well, notice that the Log $\alpha$-Norm metric ($\log\Vert\mathbf{W}\Vert_{\alpha}^{\alpha}$) performs best (with an RMSE of $0.42$, see Table~\ref{table:cv-models}); and the Weighted Alpha metric ($\hat\alpha =\alpha\log\lambda_{max} $), which is an approximation to the Log $\alpha$-Norm metric~\cite{MM20_unpub_work}, performs second best (with an RMSE of $0.48$, see Table~\ref{table:cv-models}).

@@

\begin{table}[t]
\small
\begin{center}
%\begin{tabular}{|p{1in}|c|c|c|c|c|}
\begin{tabular}{|p{0.75in}|c|c|c|c|c|}
%\begin{tabular}{|l|c|c|c|c|c|}
\hline
 Series    &\#   & $\log\langle\Vert\mathbf{W}\Vert_{F}\rangle$ & $\log\langle\Vert\mathbf{W}\Vert_{\infty}\rangle$ & $\hat{\alpha}$ & $\log\langle\Vert\mathbf{X}\Vert^{\alpha}_{\alpha}\rangle$ \\
\hline
 VGG       &  6 & 0.56 & 0.53 & 0.48          & \textbf{0.42}  \\
 ResNet    &  5 & 0.9  & 1.4  & \textbf{0.61} & 0.66           \\
 ResNet-1K & 19 & 2.4  & 3.6  & \textbf{1.8}  & 1.9            \\
 DenseNet  &  4 & 0.3  & 0.26 & \textbf{0.16} & 0.21           \\
\hline
\end{tabular}
\end{center}
\caption{RMSE (smaller is better) for linear fits of quality metrics to Reported Top1 Test Error for pretrained models in each architecture series.  VGG, ResNet, and DenseNet were pretrained on ImageNet, and ResNet-1K was pretrained on ImageNet-1K. 
\michael{double check numbers}
}
\label{table:cv-models}
\end{table}

@@

More generally, we can understand Figure~\ref{fig:vgg-alpha-layers} in terms of the \emph{Correlation Flow}. 
Recall that the log $\alpha$-Norm metric and the Weighted Alpha metric are based on HT-SR Theory~\cite{MM18_TR, MM19_HTSR_ICML, MM20_SDM}, which is in turn based on ideas from the statisical mechanics of heavy tailed and strongly correlated systems~\cite{BouchaudPotters03, SornetteBook, BP11, bun2017}. 
There, one expects the weight matrices of well-trained DNNs will 
exhibit correlations over many size scales. Their ESDs can be well-fit by a (truncated) Power law (PL), with exponents $\alpha\in[2,4]$.
Much larger values $(\alpha\gg 5\;or\;6)$ may relfect poorer PL fits, whereas smaller values $(\alpha\rightarrow 2)$, are associated with models
that generalize better.
%, but the presence of many adjacent layers with relatively good PL fits \emph{suggests} that those adjacent layers ``impedance match'' well and that the correlations that are captured by one layer propagate well to subsequent layers.
Informally, one would expect a DNN model to perform well when it fascilitates the propagation of information/features across layers.
Previous studies argue this by computing the gradients over the input data.
In the absence of training/test data, we can to try to quantify this by measuring the PL properties of empirical weight matrices.
Smaller $\alpha$ values correspond to layers in which correlations across multiple scales are better captured~\cite{MM18_TR,SornetteBook}, and thus we expect that small values of $\alpha$ that are stable across multiple layers enable better \emph{correlation flow} through the network.

%\paragraph{Layer Analysis: Behavior on Less Thoroughy Studied CV Models.}
\paragraph{Correlation Flow: PL vs. Norm Metrics.}

@@

\begin{figure}[t]
   \centering
   \subfigure[$\lambda_{max}$ for ResNet20 layers]{
      %\includegraphics[scale=0.14]{img/resnet4d_maxev.png}
      \includegraphics[width=4.0cm]{img/resnet4d_maxev.png}
      %\includegraphics[width=4.5cm]{img/resnet4d_maxev.png}
      \label{fig:resnet204Dmaxev}
   }
   %\qquad
   \subfigure[$\alpha$ for ResNet20 layers]{
      %\includegraphics[scale=0.14]{img/resnet4d_alphas.png}
      \includegraphics[width=4.0cm]{img/resnet4d_alphas.png}
      %\includegraphics[width=4.5cm]{img/resnet4d_alphas.png}
      \label{fig:resnet204Dalpha}
   }
   \caption{Correlation Flow.
            ResNet20, distilled with Group Regularization, as implemented in the \texttt{distiller} (4D\_regularized\_5Lremoved) pre-trained models.  
            Spectral Norm, $\log\lambda_{max}$, and, PL exponent, $\alpha$, for individual layer, versus layer id, for both baseline (before distillation, green) and finetuned (after distillation, red) pre-trained models. 
           }
   \label{fig:resnet204D5L}
\end{figure}

\paragraph{Scale Collapse; or, Distillation may break models}

In examining hundreds of pretrained models, we have found several anamolies that demonsrate the power of our approach.
Here, we demonstrate that some distillations methods may actually \emph{break} models unexpectedly by introducing what we call \emph{Scale Collapse},
where several distilled layers have unexpectedly small Spectral Norms.
We consider ResNet20, trained on CIFAR10, before and after applying the Group Regularization distillation technique, as implemented in the \texttt{distiller} package.%
\footnote{For details, see \url{https://nervanasystems.github.io/distiller/\#distiller-documentation} and also \url{https://github.com/NervanaSystems/distiller}.}
We analyze the pre-trained 4D\_regularized\_5Lremoved baseline and finetuned models.  %\cite{distiller_repo}.
The reported baseline test accuracies ($Top1=91.45$ and $Top5=99.75$) are better than the reported finetuned test accuracies ($Top1=91.02$ and $Top5=99.67$)~\cite{XXX-XXX}.  Because the baseline accuracy is greater,  the previous results on ResNet (Table~\ref{table:cv-models} and Figure~\ref{fig:cv2-accuracy}) suggests that the baseline Spectral Norms should be \emph{smaller} on average than the finetuned ones should be smaller.
\emph{The oppopsite is observed.}
%\michael{Do we have something backwards here: where we observed that the average norm to increase with decreasing test error (as it ``should'' not), whereas the average PL exponent $\alpha$ decreases (as ``expected'' from HT-SR Theory).  }
%In both cases (Frobenius norm results not shown), we observe the opposite.
Figure~\ref{fig:resnet204D5L} presents the Spectral Norm (here denoteds $\log\lambda_{max}$) and PL exponent ($\alpha$) for each individual layer weight matrix $\mathbf{W}$.%
\footnote{Here, we only include layer matrices or feature maps with $M\ge50$.}
On the other hand, the $\alpha$ values do not differ systematically between the baseline and finetuned models.
%\michael{Some comment about big jump in norm; but fix previous backwards question first.}--SEE BELOW
Also (not shown), the average (unweighted) baseline $\alpha$ is \emph{smaller} than the finetuned average (as predicted by HT-SR Theory, the basis of $\hat{\alpha}$).

Note that Figure ~\ref{fig:resnet204Dalph} depcits 2 very large $\alpha\gg 6$ for the baseline model, but not for the finetuned model.
This suggests that the baseline model has at least 2 over-parameterized layers, and the distillation method does, in fact, 
improve the finetuned model by compressing these layers.s

\michael{XXX.  WORK ON THIS PAR AFTER DO NLP EXAMPLES.}
Our interpretation of this is the following.
The pre-trained models in the \texttt{distiller} package have passed some quality metric, but they are much less well trodden than any of the 
VGG, ResNet, or DenseNet series we cosidered above.
\charles{MOvE THIS SOMEWHERE ELSE AND CLEAN UP THIS SECTION Notice while norms make good regularizers for a single model, there is no reason \emph{a priori} 
to expect them correlate so well with the test accuracies across different models.
However, we do expect the PL $\alpha$ to do so because it effectively measures the amount of correlation in the model}
%
The reason for this is that the \texttt{distiller} Group Regularization technique 
%%has the unusual effect of increasing
\nred{spuriously increases}
 the norms of the $\mathbf{W}$ pre-activation maps for at least two of the Conv2D layers.
\michael{This impedance shuffling or whatever it is called messes up norms, but the strong correlations are still preserved, as seen in the $\hat{\alpha}$ metric, and the model quality is good.  CLARIFY.}
\michael{XXX.  INTERPRET IN TERMS OF XXX GOOD VERSUS BAD, AS OPPOSED TO GOOD BETTER BEST.}

### 2020-02-08 methods.tex
updated main sections

For the \emph{Weighted Alpha metric}, we average of $\hat{\alpha}$ over all layers, i.e., 
$ %$$
\sum_l \hat{\alpha}_l = \sum_l \alpha_l\log\lambda_{max,l}  .  
$ %$$
\michael{Be careful to get right.}
The Weighted Alpha metric was introduced previously~\cite{MM20_SDM}, where (on a much more limited dataset than we consider here) it was shown to correlate well with trends in reported test accuracies of pretrained DNNs.
Based on this, in this paper, we introduce and evaluate the $\alpha$-Norm metric.
One would expect $\hat{\alpha}$ to approximate the log $\alpha$-Norm very well for $\alpha < 2$ and reasoably well for $\alpha\in[2,5]$~\cite{MM20_unpub_work}.

To avoid confusion, let us clarify the relationship between $\alpha$ and $\hat{\alpha}$.  
We fit the ESD of the correlation matrix $\mathbf{X}$ to a truncated PL, parameterized by 2 values: the PL exponent $\alpha$, and the maximum eigenvalue $\lambda_{max}$.  
(Technically, we also need the minimum eigenvalue $\lambda_{min}$, but this detail does not affect our analysis.)
The PL exponent $\alpha$ measures of the amount of correlation in a DNN layer weight matrix $\mathbf{W}$. 
It is valid for $\lambda<\lambda_{max}$, and it is scale-invariant, i.e., it does not depend on the normalization of $\mathbf{W}$ or $\mathbf{X}$.
The $\lambda_{max}$ is a measure of the size of $\mathbf{W}$.
%
Multiplying each $\alpha$ by the corresponding $\log\lambda_{max}$ weighs ``bigger'' layers more, and averaging this product leads to a balanced, Weighted Alpha metric for the entire~DNN.  
%%%
%%For small values of $\alpha$, this Weighted Alpha metric approximates the log $\alpha$-Shatten norm, as can be shown with a statistical mechanics and random matrix theory derivation \cite{MM20_unpub_work}.
%%%
%%The Weighted Alpha metric and $\alpha$-Shatten norm metric also often behave like an improved, weighted log average Spectral Norm, and may track this metric in some cases.

>>>>

For the \emph{Weighted Alpha metric}, we average of $\hat{\alpha}$ over all layers, i.e., 
$ %$$
\sum_l \hat{\alpha}_l = \sum_l \alpha_l\log\lambda_{max,l}  .  
$ %$$
%\michael{Be careful to get right.}
The Weighted Alpha metric was introduced previously~\cite{MM20_SDM}, where it was shown to correlate well with trends in reported test accuracies of pretrained DNNs, albeit on a limited set of models.
Based on this, in this paper, we introduce and evaluate the $\alpha$-Norm metric.
One would expect $\hat{\alpha}$ to approximate the log $\alpha$-Norm very well for $\alpha < 2$ and reasoably well for $\alpha\in[2,5]$~\cite{MM20_unpub_work}.

To avoid confusion, let us clarify the relationship between $\alpha$ and $\hat{\alpha}$.  
We fit the ESD of the correlation matrix $\mathbf{X}$ to a truncated PL, parameterized by 2 values: the PL exponent $\alpha$, and the maximum eigenvalue $\lambda_{max}$.  
%(Technically, we also need the minimum eigenvalue $\lambda_{min}$, but this detail does not affect our analysis.)
The PL exponent $\alpha$ measures of the amount of correlation in a DNN layer weight matrix $\mathbf{W}$. 
It is valid for $\lambda<\lambda_{max}$, and it is scale-invariant, i.e., it does not depend on the normalization of $\mathbf{W}$ or $\mathbf{X}$.
The $\lambda_{max}$ is a measure of the size, or scale, of $\mathbf{W}$.
%
Multiplying each $\alpha$ by the corresponding $\log\lambda_{max}$ weighs ``bigger'' layers more, and averaging this product leads to a balanced, Weighted Alpha metric for the entire~DNN.  
%%%
%%For small values of $\alpha$, this Weighted Alpha metric approximates the log $\alpha$-Shatten norm, as can be shown with a statistical mechanics and random matrix theory derivation \cite{MM20_unpub_work}.
%%%
%%The Weighted Alpha metric and $\alpha$-Shatten norm metric also often behave like an improved, weighted log average Spectral Norm, and may track this metric in some cases.

### 2020-02-08 nlp_models.tex
updated main sections

\section{Comparison of NLP Transformer Models}
\label{sxn:nlp}

@@

\charles{More details here.}
The GPT models we analyze are deployed with the popular HuggingFace PyTorch library~\cite{XXX-XXX}.
GPT has 12 layers, with 4 Multi-head Attention Blocks, giving $48$ layer Weight Matrices $\mathbf{W}$.
Each Block has 2 components, the Self Attention (attn) and the Projection (proj) matrics.  
The self-attention  matrices are larger, of dimension ($2304\times 768$) or ($3072\times 768$).
The projection layer concatenates the self-attention results into a vector (of dimension $768$).
This gives $50$ large matrices.
%
Because GPTand GPT2 are trained on different data sets, the initial Embedding matrices differ in shape.
GPT has an initial Token and Positional Embedding layers, of dimension $(40478\times 768)$ and $(512\times 768)$, respectively, whereas GPT2 has input Embeddings of shape $(50257\times 768)$ and $(1024\times 768)$, respectively. 
%
The OpenAI GPT2 (English) models are: \nred{GPT2-small, GPT2-medium, GPT2-large, and GPT2-xl}, \
having include $12, 24, 36, \text{and }48$ layers, respectively, with increasingly larger weight matrices.
The model card for GPT2 is published on github.\footnote{\url{https://github.com/openai/gpt-2/blob/master/model_card.md}}.

%        &  Num.  & $\Vert\mathbf{W}\Vert_{F}$ & $\Vert\mathbf{W}\Vert_{2}$ & $\hat{\alpha}$ & $\Vert\mathbf{X}\Vert^{\alpha}_{\alpha}$ \\
% Series & Models & Metric                     & Metric                     & Metric         & Metric                                   \\

\begin{table}[t]
\small
\begin{center}
%\begin{tabular}{|p{1in}|c|c|c|c|c|}
\begin{tabular}{|p{0.75in}|c|c|c|c|c|}
\hline
%   &    & Frobenius Norm & Spectral Norm & Weighted Alpha & Alpha Norm \\
% Series & \#Layers   & $\Vert\mathbf{W}\Vert_{F}$ & $\Vert\mathbf{W}\Vert_{\infty}$ & $\hat{\alpha}=\alpha\log\lambda_{max}$ & $\Vert\mathbf{X}\Vert^{\alpha}_{\alpha}$ \\
        &        & log                   & log                        & Weighted       & log                                 \\
        & Num.   & $\Vert\cdot\Vert_{F}$ & $\Vert\cdot\Vert_{\infty}$ & $\hat{\alpha}$ & $\Vert\cdot\Vert^{\alpha}_{\alpha}$ \\
 Series & Layers & Metric                & Metric                     & Metric         & Metric                              \\
\hline
GPT & 49 & 1.64  & 1.72 & 7.01 & 7.28 \\
GPT2-small & 49 & 2.04  & 2.54& 9.62 & 9.87 \\
\hline
GPT2 medium & 98 & 2.08 & 2.58& 9.74 & 10.01 \\
GPT2 large & 146 & 1.85 & 1.99& 7.67 & 7.94 \\
GPT2 xl & 194 & 1.86 & 1.92 & 7.17 & 7.51 \\
\hline
\end{tabular}
\end{center}
\caption{Average value for the Average log Norm metrics and the Weighted Alpha metric for pretrainnd OpenAI GPT and GPT2 models.  }
\label{table:nlp}
\end{table}

>>>>

\section{Comparison of NLP Models}
\label{sxn:nlp}

@@

\charles{More details here.}
The GPT models we analyze are deployed with the popular HuggingFace PyTorch library~\cite{XXX-XXX}.
GPT has 12 layers, with 4 Multi-head Attention Blocks, giving $48$ layer Weight Matrices $\mathbf{W}$.
Each Block has 2 components, the Self Attention (attn) and the Projection (proj) matrics.  
The self-attention  matrices are larger, of dimension ($2304\times 768$) or ($3072\times 768$).
The projection layer concatenates the self-attention results into a vector (of dimension $768$).
This gives $50$ large matrices.
%
Because GPTand GPT2 are trained on different data sets, the initial Embedding matrices differ in shape.
GPT has an initial Token and Positional Embedding layers, of dimension $(40478\times 768)$ and $(512\times 768)$, respectively, whereas GPT2 has input Embeddings of shape $(50257\times 768)$ and $(1024\times 768)$, respectively. 
%
The OpenAI GPT2 (English) models are: \nred{GPT2-small, GPT2-medium, GPT2-large, and GPT2-xl}, \
having include $12, 24, 36, \text{and }48$ layers, respectively, with increasingly larger weight matrices.
%The model card for GPT2 is published on github.\footnote{\url{https://github.com/openai/gpt-2/blob/master/model_card.md}}.

\begin{table}[t]
\small
\begin{center}
%\begin{tabular}{|p{1in}|c|c|c|c|c|}
\begin{tabular}{|p{0.75in}|c|c|c|c|c|}
\hline
 Series  & \#   & $\langle\log\Vert\mathbf{W}\Vert_{F}\rangle$ & $\langle\log\Vert\mathbf{W}\Vert_{\infty}\rangle$ & $\hat{\alpha}$ & $\langle\log\Vert\mathbf{X}\Vert^{\alpha}_{\alpha}\rangle$ \\
\hline
GPT & 49 & 1.64  & 1.72 & 7.01 & 7.28 \\
GPT2-small & 49 & 2.04  & 2.54& 9.62 & 9.87 \\
\hline
GPT2 medium & 98 & 2.08 & 2.58& 9.74 & 10.01 \\
GPT2 large & 146 & 1.85 & 1.99& 7.67 & 7.94 \\
GPT2 xl & 194 & 1.86 & 1.92 & 7.17 & 7.51 \\
\hline
\end{tabular}
\end{center}
\caption{Average value for the Average log Norm metrics and the Weighted Alpha metric for pretrainnd OpenAI GPT and GPT2 models. Column \# refers to number of layers treated.  Note averages do not include the first embedding layer(s) because they are not (implicitly) normalized.  }
\label{table:nlp}
\end{table}
